---
output:
  pdf_document: default
  html_document: default
---
```{r, echo=FALSE}
source("links.R")
```

# Knowledge basket: Writing and peer feedback

## General instructions {#writinggeneral}
The module writing and peer feedback activities have three stages.

-   **Create** phase due the first Friday of the module at 3:03 p.m. ET

-   **Assess** phase due the second Tuesday of the module at 3:03 p.m. ET

-   __Reflect__ phase due the second Friday of the module at 3:03 p.m. ET

### Create phase

The **Create** phase is due the first Friday of the module at 3:03 p.m. ET

-   Spend \~30 minutes writing a response to the prompt.

-   Write about 200--500 words. The word count isn't strict, but the submission requirements listed below ARE.

    -   The prompt should be clearly and comprehensively addressed.

    -   Your writing should be in full sentences and be broken into paragraphs as appropriate.

    -   Any grammatical or word choice errors should be minimal and not obstruct the meaning.

    -   There is a clear central idea that is well summarized in a concluding sentence(s).

    #### Submission requirements

    Your submission should be:

    -   typed (not handwritten)

    -   no more than one page

    -   single-spaced

    -   size 12 font

    -   margins should be no larger than 1 inch

    -   saved as a PDF

### Assess phase

The **Assess** phase is due the second Tuesday of the module at 3:03 p.m. ET

You will need to assess TWO of your peers in this phase. You will be asked:

-   if they have met the submission requirements,

-   to rate them on the rubric,

-   to make a short comment about a strength of this piece of writing,

-   to make a short comment about a way this piece of writing could be improved.

### Reflect phase

The **Reflect** phase is due second Friday of the module at 3:03 p.m. ET

-   Read the feedback received from your peers.

-   Rate the usefulness on a 3-point scale.

### General instructions

These assessments can be used to make up your knowledge basket. They are also useful in helping you prepare for your portfolio writing samples and final project writing.

Warning: MAKE SURE YOU CLICK SUBMIT! Check that each phase is showing as submitted. Students  have occasionally struggled with this in peerScholar's interface and no regrades/adjustments will be possible after the fact.

Your mark for this assessment will be based on participation. There will be separate marks for each phase, i.e., you can get part marks overall. 45% for completing create, 45% for completing assess, 10% for completing reflect. Please note that participation not in the spirit of the assessment (e.g. just putting the Lorem Ipsum text, or giving feedback like "write better" and nothing else) will not get you marks. 


## Module 1 writing task

+--------------------------------------------------------+----------------------------------------------------+
| **Information**                                        | **Note**                                           |
+:=======================================================+:===================================================+
| Name                                                   | Module 1 writing task                      |
+--------------------------------------------------------+----------------------------------------------------+
| Type (Main, Mini or Basket)                              | Basket                                             |
+--------------------------------------------------------+----------------------------------------------------+
| Value                                                  | 0.5% (0.245%, 0.245%, 0.01%) <br> Completion                                           |
+--------------------------------------------------------+----------------------------------------------------+
| Due                                                    | __Create phase__: `r m1_c`;  <br> __Assess phase__: `r m1_a`; <br> __Reflect phase__: `r m1_r`;                                |
+--------------------------------------------------------+----------------------------------------------------+
| Submission instructions                                | Submission: [Via peerScholar](`r m1_link`)                |
|                                                        |                                                    |
|                                                        | Marked for completion              |
+--------------------------------------------------------+----------------------------------------------------+
| Late submissions, accommodations, and extension policy | No late submissions, accommodations, or extensions. |
+--------------------------------------------------------+----------------------------------------------------+

### M1 Instructions

Make sure you are familiar with the [general instructions](#writinggeneral) for these types of tasks.

#### M1 Prompt

Discuss what you consider the most important dos and don'ts when giving peer feedback. What will make your peers' feedback most valuable to you?


#### M1 Rubric

<br>

<br>

```{r, echo=FALSE, message=FALSE}
require(tidyverse)
pd_prop_rubric <- read_csv("rubrics/m1-writing.csv") 

if (knitr:::is_latex_output()) {
  pd_prop_rubric %>% 
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling(latex_options = c("striped"), font_size = 8) %>% 
        kableExtra::column_spec(2:5, width = "12em") 
  
  
} else {
 pd_prop_rubric %>% 
  kableExtra::kable() %>%
  kableExtra::kable_styling() %>% 
  kableExtra::scroll_box(width = "100%")
}

```

## Module 2 writing task

+--------------------------------------------------------+----------------------------------------------------+
| **Information**                                        | **Note**                                           |
+:=======================================================+:===================================================+
| Name                                                   | Module 2 writing task                      |
+--------------------------------------------------------+----------------------------------------------------+
| Type (Main, Mini or Basket)                              | Basket                                             |
+--------------------------------------------------------+----------------------------------------------------+
| Value                                                  | 0.5% (0.245%, 0.245%, 0.01%) <br> Completion                                           |
+--------------------------------------------------------+----------------------------------------------------+
| Due                                                    | __Create phase__: `r m2_c`;  <br> __Assess phase__: `r m2_a`; <br> __Reflect phase__: `r m2_r`;                                |
+--------------------------------------------------------+----------------------------------------------------+
| Submission instructions                                | Submission: [Via peerScholar](`r m2_link`)                |
|                                                        |                                                    |
|                                                        | Marked for completion              |
+--------------------------------------------------------+----------------------------------------------------+
| Late submissions, accommodations, and extension policy | No late submissions, accommodations, or extensions. |
+--------------------------------------------------------+----------------------------------------------------+

### M2 Instructions

Make sure you are familiar with the [general instructions](#writinggeneral) for these types of tasks.

#### M2 Prompt

Read [*Science isn't broken* (Aschwanden, 2015)](https://fivethirtyeight.com/features/science-isnt-broken/) using the *previewing* and *skimming* strategy outlined below. Discuss what you learn from the article, with a focus on what you **notice about your own thinking** when playing with the *"Hack Your Way To Scientific Glory*" interactive. Make sure you paraphrase appropriately (see [Module 2 paraphrasing section](#paraphrasing)) and add the reference for the article. (It is okay to put the reference by itself on a second page, if required.) 

Instead of reading from beginning to end try ***previewing*** and then ***skimming*** to be faster:

1.  Read the **title**. Pay attention to the "Filed Under" and date of publication.

   🤔*Why do you think we have assigned this reading to you?*

2.  Skip the text until the **interactive figure** called "*Hack Your Way To Scientific Glory*".

When you change political party in section 1, or other items in section 2, how does the p-value change in section 4 of the interactive figure?

   🤔*What do you understand from this figure? What do you notice about your own thinking as you play with it?*

**Tip:** Reading one paragraph before and after a figure helps clarify the figure.

3.  Skip the text until the **figure** of the football field.

   🤔 *What do you understand from this figure?*

4.  Skip the text until the **figure** called "*Same Data, Different Conclusions*".

   🤔 *What do you understand from this figure?*

6.  Read the two **bolded quotes**: "*Science is great, but*..." and "*Human fallibilities*...".

7.  Read the **last paragraph** (often the concluding paragraph).

8.  Now write your **200--500-word reflection** on what you have learned.

    -   **Paraphrase!** That is, use your own words, don't copy/paste. Use the [paraphrasing how-to from the week 2 module](https://q.utoronto.ca/courses/204826/pages/w2-paraphrasing "W2 Paraphrasing") to help you.

    -   Discuss what you noticed about your thinking while playing with the *Hack Your Way To Scientific Glory*" interactive.

    -   Include a **conclusion** at the end.

    -   Use in-text **citation** as follows (Aschwanden, 2015) and put the reference at the end.

9. Go back and read the entire text to see if your understanding was correct.

##### M2 Reference

Aschwanden, C. (2015). *Science Isn't Broken: It's just a hell of a lot harder than we give it credit for*. Retrieved from [https://fivethirtyeight.com/features/science-isnt-broken](https://fivethirtyeight.com/features/science-isnt-broken)

#### M2 Rubric

```{r, echo=FALSE, message=FALSE}
require(tidyverse)
rubric <- read_csv("rubrics/m2-writing.csv") %>% 
  filter(!is.na(Component))

if (knitr:::is_latex_output()) {
  rubric %>% 
  kableExtra::kable(booktabs = T) %>%
  kableExtra::kable_styling(latex_options = c("striped"), font_size = 8) %>% 
        kableExtra::column_spec(2:5, width = "12em") 
  
  
} else {
 rubric %>% 
  kableExtra::kable() %>%
  kableExtra::kable_styling() %>% 
  kableExtra::scroll_box(width = "100%")
  }

```
